target_offtarget

### 2025-04-13 manuscript_figures.Rmd
Update Figures S1 and S2

@@

## Figure S1

@@

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_S1.pdf",
       width = 12,
       height = 8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S1.png",
       width = 12,
       height = 8)

pool_norm1_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray") 
  ) +
  ylab("Log (viral reads/cleaned reads)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

pool_norm2_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (viral reads/cleaned reads/genome length)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

### ***Final plot***
```{r}
ggarrange(
  pool_counts_sum,
  pool_norm1_sum,
  pool_norm2_sum,
  pool_depths_sum,
  nrow = 2,
  ncol = 2,
  common.legend = TRUE, 
  align = "hv"
)

@@

# pivot longer  
dedup_long <-
  contingency_dedup |>
  filter(!genus %in% contaminants) |>
  filter(genus != "NA") |>
  pivot_longer(cols = A:P,
               names_to = "Sample_id",
               values_to = "count") |>
  mutate(
    target = case_when(
      genus == "Cyclovirus" ~ "off_target",
      genus == "Cardiovirus" ~ "off_target",
      genus == "Kobuvirus" ~ "off_target",
      .default = "on_target"
    )
  ) |>
  mutate(genome_structure = case_when((genus == "Mastadenovirus" |
                                         genus == "Cytomegalovirus") ~ "DNA",
                                      .default = "RNA"
  ))

no_dedup_long <- contingency_nodedup |>
  filter(!genus %in% contaminants) |>
  filter(genus != "NA") |>
  pivot_longer(cols = A:P,
               names_to = "Sample_id",
               values_to = "count") |>
  mutate(
    target = case_when(
      genus == "Cyclovirus" ~ "off_target",
      genus == "Cardiovirus" ~ "off_target",
      genus == "Kobuvirus" ~ "off_target",
      .default = "on_target"
    )
  ) |>
  mutate(genome_structure = case_when((genus == "Mastadenovirus" |
                                         genus == "Cytomegalovirus") ~ "DNA",
                                      .default = "RNA"
  ))

>>>>

### --------------------
## Figure S1

pool_norm1_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(norm_counts1),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray") 
  ) +
  ylab("Log (viral reads/cleaned reads)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

pool_norm2_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = norm_counts2,
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (viral reads/cleaned reads/genome length)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

### ***Final plot***
```{r}
ggarrange(
  pool_counts_sum,
  pool_depths_sum,
  nrow = 1,
  ncol = 2,
  common.legend = TRUE, 
  align = "hv"
)

ggsave("figures/manuscript_figure_2025/PDF/Figure_S1.pdf",
       width = 12,
       height = 4)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S1.png",
       width = 12,
       height = 4)

@@

@@

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

@@

# pivot longer  
dedup_long <-
  contingency_dedup |>
  filter(!genus %in% contaminants) |>
  filter(genus != "NA") |>
  pivot_longer(cols = A:P,
               names_to = "Sample_id",
               values_to = "count") |>
  mutate(
    target = case_when(
      genus == "Cyclovirus" ~ "off_target",
      genus == "Cardiovirus" ~ "off_target",
      genus == "Kobuvirus" ~ "off_target",
      .default = "on_target"
    )
  ) |>
  mutate(genome_structure = 
           case_when((genus == "Mastadenovirus" | 
                        genus == "Cytomegalovirus" | 
                        genus == "Cyclovirus" ~ "DNA"),
                     .default = "RNA"
  ))

no_dedup_long <- contingency_nodedup |>
  filter(!genus %in% contaminants) |>
  filter(genus != "NA") |>
  pivot_longer(cols = A:P,
               names_to = "Sample_id",
               values_to = "count") |>
  mutate(
    target = case_when(
      genus == "Cyclovirus" ~ "off_target",
      genus == "Cardiovirus" ~ "off_target",
      genus == "Kobuvirus" ~ "off_target",
      .default = "on_target"
    )
  ) |>
  mutate(genome_structure = 
           case_when((genus == "Mastadenovirus" | 
                        genus == "Cytomegalovirus" | 
                        genus == "Cyclovirus" ~ "DNA"),
                     .default = "RNA"
  ))
